Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-29 WSSSPE4_report/WSSSPE4_report.tex
more little changes

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Alice~Allen$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nunez-Corrales$^{(9)}$
Anshu~Dubey$^{(10)}$,
R.~Stuart~Geiger$^(11)$,
Jonah~Miller$^{12)}$,
Emily~Chen$^{123}$,
Wolfgang~Bangerth$^{14)}$,
\\Author order to be determined based on contributions
}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Alice~Allen$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nunez-Corrales$^{(9)}$
Anshu~Dubey$^{(10)}$,
R.~Stuart~Geiger$^{(11)}$,
Jonah~Miller$^{(12)}$,
Emily~Chen$^{(13)}$,
Wolfgang~Bangerth$^{(14)}$,
\\Author order to be determined based on contributions
}
